% Example Resume — John Doe (fictional)
% Single-column article layout
% All names, companies, and metrics are invented.

\documentclass[a4,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{tikz}
\input{glyphtounicode}

% Example color scheme — dark green (fictional company brand)
\definecolor{PrimaryColor}{HTML}{1A3A2A}
\definecolor{AccentColor}{HTML}{4A7C5F}

%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace*{0pt}\color{PrimaryColor}\scshape\raggedright\large
}{}{0em}{}[\color{PrimaryColor}\titlerule \vspace*{1pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace*{1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace*{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace*{2pt} \textbf{\normalsize\color{PrimaryColor}#1} & \textit{\normalsize\color{AccentColor}#2} \\
      \textit{\normalsize#3} & \textit{\normalsize\color{AccentColor}#4} \\
    \end{tabular*}\vspace*{0pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace*{0pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\color{PrimaryColor}#1} & \textit{\color{AccentColor}#2} \\
    \end{tabular*}\vspace*{1pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace*{-1pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace*{-2pt}}

\begin{document}

%----------HEADING----------
% TWO-COLUMN HEADER (no photo) — uncomment to switch back
% \begin{minipage}[c]{0.62\textwidth}
%     \raggedright
%     \textbf{\Huge \scshape \color{PrimaryColor} John Doe} \\[10pt]
%     \textbf{\Large \scshape \color{PrimaryColor} Senior Backend Engineer}
% \end{minipage}%
% \begin{minipage}[c]{0.38\textwidth}
%     \raggedleft
%     \small Hamburg, Germany\\ [3pt]
%     \small +49 160 0000000 \\ [3pt]
%     \href{mailto:john.doe@example.com}{\small john.doe@example.com}\\ [3pt]
%     \href{https://www.linkedin.com/in/john-doe-eng/}{\small \underline{linkedin.com/in/john-doe-eng}}
% \end{minipage} \vspace*{-15pt}

% THREE-COLUMN HEADER WITH PHOTO
% Symmetric 0.43/0.14/0.43 widths center the circular photo on the page.
\begin{minipage}[c]{0.43\textwidth}
    \raggedright
    \textbf{\Huge \scshape \color{PrimaryColor} John Doe} \\[10pt]
    \textbf{\Large \scshape \color{PrimaryColor} Senior Backend Engineer}
\end{minipage}%
\begin{minipage}[c]{0.14\textwidth}
    \centering
    \begin{tikzpicture}
      \fill[gray!20] (0,0) circle (1.1cm);
      \draw[color=PrimaryColor, line width=2pt] (0,0) circle[radius=1.12cm];
      \node[font=\scriptsize\color{gray!60}] at (0,0) {Photo};
    \end{tikzpicture}
\end{minipage}%
\begin{minipage}[c]{0.43\textwidth}
    \raggedleft
    \small Hamburg, Germany\\ [3pt]
    \small +49 160 0000000 \\ [3pt]
    \href{mailto:john.doe@example.com}{\small john.doe@example.com}\\ [3pt]
    \href{https://www.linkedin.com/in/john-doe-eng/}{\small \underline{linkedin.com/in/john-doe-eng}}
\end{minipage} \vspace*{-15pt}

%-----------SUMMARY-----------
\vspace*{-6pt}
\section{Summary}
    \leftskip=0.15in \small Backend engineer with 8 years in fintech and payments infrastructure. Redesigned a core ledger service to handle 10x traffic growth and reduced settlement pipeline P99 latency from 800ms to under 120ms. Seeking a Staff or Senior Backend role where distributed systems depth is the job, not a side concern.\par\vspace*{-4pt}

%-----------EXPERIENCE-----------
\section{Experience}

  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Backend Engineer}{Jan 2020 -- Present}
      {\href{https://example.com}{\underline{FinFlow GmbH}}}{Hamburg, Germany}
      \resumeItemListStart
        \resumeItem{Redesigned the core ledger service to handle 10x traffic growth with no additional infrastructure, replacing a synchronous write path with an event-sourced model backed by Kafka.}
        \resumeItem{Reduced settlement pipeline P99 latency from 800ms to under 120ms by profiling the hot path, eliminating redundant DB round-trips, and introducing read replicas for non-critical queries.}
        \resumeItem{Led migration of 6 services out of a monolith over 18 months, coordinating 4 engineers and maintaining zero downtime throughout.}
        \resumeItem{Introduced OpenTelemetry-based distributed tracing across the payment stack; reduced mean time to diagnose production incidents from hours to under 15 minutes.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Engineer}{Mar 2018 -- Dec 2019}
      {\href{https://example.com}{\underline{ClearPay Technologies}}}{Hamburg, Germany}
      \resumeItemListStart
        \resumeItem{Owned the reconciliation service processing nightly settlement files from 12 banking partners; rewrote the parser in Go, halving processing time.}
        \resumeItem{Built an idempotency layer for the external payment API that eliminated duplicate charges during network retry storms.}
        \resumeItem{Migrated the team's deployment pipeline from manual scripts to Kubernetes-based CD; reduced deployment time from 45 minutes to under 5.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Backend Developer}{Sep 2016 -- Feb 2018}
      {\href{https://example.com}{\underline{Nordcloud AG}}}{Hamburg, Germany}
      \resumeItemListStart
        \resumeItem{Maintained and extended a Java-based billing system for a managed cloud services provider.}
        \resumeItem{Wrote the first automated integration test suite for the billing API; covered 80\% of the critical payment paths within 3 months.}
        \resumeItem{Participated in on-call rotation; documented 15 recurring incident types and built runbooks that reduced escalations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BSc Computer Science}{Hamburg, Germany}
      {\href{https://www.uni-hamburg.de/en/}{\underline{University of Hamburg}}}{Oct 2012 -- Sep 2016}
      \resumeItemListStart
        \resumeItem{Thesis: Optimising lock contention in concurrent key-value stores.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Rust, Python, Java, SQL} \vspace*{2pt} \\
     \textbf{Infrastructure}{: Kafka, PostgreSQL, Kubernetes, Redis, gRPC} \vspace*{2pt} \\
     \textbf{Observability}{: OpenTelemetry, Prometheus, Grafana, Jaeger} \vspace*{2pt} \\
     \textbf{Certifications}{: \href{https://example.com/cert}{\underline{Certified Kubernetes Administrator (CNCF)}}, \href{https://example.com/cert}{\underline{AWS Solutions Architect}}}
    }}
 \end{itemize}

%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
          \textbf{English --- C2 Level (Native)} \vspace*{2pt} \\
          \textbf{German --- B1 Level (Conversational)} \vspace*{2pt} \\
    }}
 \end{itemize}

\end{document}
